    \chapter{Feasibility Study}
        \section{Technical Feasibility}
        We have required hardware i.e computer with good GPU and 32GB RAM and some test programmes can also be run in Google Colaboratory. So there is no problem with hardware devices.\\
        We are using python for development of the system, and all the team members are familiar in the language. All other utility softwares being used are all free of cost and easy to use. So there is no problem with language and softwares.\\
        As for datasets to train our GAN model, we have collected some datasets from internet and filtered and processed them as per our need. If necessary we can prepare our own datasets as per required. So, there seems no problem with datasets too.\\
        So the project is technically feasible.
        \section{Operational Feasibility}
        As for operational feasibility, the final system prepared will run in normal CPU. The system will be interactive, with user friendly interface and easy to operate.        
        \section{Economic Feasibility}
        For development of the system, all softwares decided to be use are all free of cost and hardware that is currently with us can be used for training model.\\
        Deployment of the system will be smooth in low end PC too so the deployment will not be much expensive. Also, the project can also be developed to business level.\\
        So,the project is economically feasible since there seems no problem with the economy for the project until now.
        % \section{Scheduling Feasibility}


