      \chapter{Requirement Analysis}
        \section{Software Requirement}
            Software requirement for our prepared system includes:
            \begin{enumerate}
                \item Python
                \item Star UML
                \item Visual Studio Code
                \item Google Colaboratory
                \item CUDA
                \item Git
	            \item Slack
                \item Texmaker
                \item Beamer
                \item Clickup
                \item Microsoft Team
                \item Google Drive
                \item Google Calender
                \item Docker
            \end{enumerate}
                
         \section{Hardware Requirement}
            Our project required following hardware requirements:
            \begin{enumerate}
                \item Desktop with NVIDIA Graphics Card (12 GB,RTX 3060 ) and 32GB RAM.
            \end{enumerate}
            
        \section{Functional Requirement}
            The functional requirements for the prepared systems are:
            \begin{enumerate}
                \item The prepared system must be able to generate appropriate designs of footprints, room splits, furnishing and room rendering and allow end users to choose preferred designs.
            \end{enumerate}

        \section{Non-Functional Requirement}
            These are essential for the better performance of the system. The points below focus on the non-functional requirements of the system going to be prepared. 
            \subsection{Reliability }
                The system should be reliable. The system should consider all necessary rooms and furnitures that must be present in a normal house.
            \subsection{Maintainability} 
                A maintainable system is required.  
            \subsection{Performance}
                The system should prepare designs quickly as possible in implementation phase.
            \subsection{Accuracy}
                The system must accurately estimate the total cost of implementing the floor plan. And,the dimentions of every corners must be accurate too. 