\chapter{Overall Description}
	\section{Top Level Requirements}
		Some top level requirements of the project are:
		\begin{enumerate}
			\item Home page with brief introductions of the crew
			\item Publish Notice
			\item Scouting Blogs
			\item Success Stories
			\item History of Crew
			\item Photo Gallery 
			\item Crew members
			\item Display friend organizations and sponsors
			\item Collect subscribers
			\item Collect enquiries
			\item Join-crew form to collect enthusiasts who wants to join crew 
		\end{enumerate}
	\section{Intended Pages and Components}
		Some list of intended pages and components in the pages are:
		\begin{enumerate}
			\item Home Page
			\begin{enumerate}
				\item Banner
				\item Message from Administratives
				\item Some Images of Different Activities
				\item Brief Crew Information
				\item Well Wishers
				\item Social Media
				\item Subscribers
				\item List of sponsors, Friend Organizations
				\item Footer
				\item Join Crew Button
			\end{enumerate}
			\item Success Stories
			\item Notice
			\item Scouting Blogs
			\item Enquiry
			\item History
			\item Direction(Map)
			\item Join Crew Form
			\item About Crew
		\end{enumerate}
		Common Columns on all the tables in the database are:
		\begin{enumerate}
			\item Id
			\item Status (Active or Passive)
			\item Created\_date 
			\item Updated\_date 
			\item Added\_by
		\end{enumerate}
		\subsection{Home Page}
		Contains some brief introduction about the crew and some updates the audience would like to get. Some major portions of the page are:
			\subsubsection{Banner}
				Contains the cover image of the crew. It may be group photo or the banner of some latest events. Contains single image of size 1920 * 1080.
			\subsubsection{Message from Administratives}
				Contains messages from Rover Leader, Chairman and some high level members of the crew. Requirements for this sections are:
				\begin{enumerate}
					\item Name
					\item Designation
					\item Photo
					\item Message
				\end{enumerate}
			\subsubsection{Recent Activities}
				Contains images of some recent highlight activities done in crew. Requirements for this section are:
				\begin{enumerate}
					\item title (of the activity)
					\item image (of the activity)
				\end{enumerate}
			\subsubsection{Brief Crew Information}
				Contains some informations about why u should join the crew. It is displayed at different places in the page in different forms.
			\subsubsection{Well Wishers}
				Contains list of well wishers of the organizations. Four well wishers are displayed in this section. Requirements for this section are:
				\begin{enumerate}
					\item Name
					\item Designation
					\item Photo
					\item Company\_logo
					\item Description(Some text by him for the crew)
				\end{enumerate}
			\subsubsection{Social Media}
				This section contains social media liks of the crew which the audiences can easily access.
				\subsubsection{Subscribers}
				This section is to collect subscriber's emails to send updates of the crew like news, blogs, notice and success stories to them through email. Requirements of this section are:
				\begin{enumerate}
					\item email (collected from a single form with 'email' as input and 'subscribe' button to submit the email.)
				\end{enumerate}
			\subsubsection{Friend Organizations}
				This section contains list of related organizations, friend organizations and sponsors of the crew. Requirements of this section are:
				\begin{enumerate}
					\item Name
					\item Location
					\item Grey image in PNG Format
					\item Color image in PNG Format
				\end{enumerate}
			\subsubsection{Footer}
				This section consists of some handy links to different sections and pages of the organizations the audience might want to visit. Contains direction and address of the crew too.
			\subsubsection{Join Crew Button}
				This button at different places in the page simply redirects the users to a form to fill to join the crew if he is interested to join the crew.
		\subsection{Notice}
		This page contains all the formal notices issuses by the crew. Requirements for posting a notice are:
		\begin{enumerate}
			\item Title of the Notice
			\item Image of the Notice (Image is scanned form of the notice published with letter head of the crew.)
		\end{enumerate}

		\subsection{Scouting Blogs}
		This page contains blogs related to scouting and scouting life, written by members of the crew to share their knowledge and experiences to the audiences and wel wishers. The fields required for a blog are:
		\begin{enumerate}
			\item Title
			\item Author
			\item Date of Publish
			\item Related Images
			\item Contents
		\end{enumerate}

		\subsection{Success Stories}
		This page contains success stories of the members of the crew where they have gain success in any part of their life with the skills and knowledge they have gained in their scouting life. The fields required for a success stories are:
		\begin{enumerate}
			\item Title
			\item Author
			\item Date of Publish
			\item Related Images
			\item Contents
		\end{enumerate}

		\subsection{Enquiry}

		